### 2019-08-19 reports/thesis/chapters/5_inference.tex
Adjust figures in DefectAlt

An experiment was conducted to investigate the specificity of the test before and after filtering. A $256\times 256$ Gaussian image with speckle defect with density $\pi_1=0.1$ and various values of $\mu_1$ were investigated. Before the experiment, various baselines were obtained. An image with a defect was simulated and then tested to obtain the ROC area, type 1 error, type 2 error and the FDR. The image was than contaminated and tested to obtain the 4 measurements again. This was repeated 300 times to obtain the empirical distribution of the AUC, type 1 error, type 2 error and FDR when testing on a un/contaminated image with defects. The ROC area, type 1 error, type 2 error and FDR were measured when testing on a filtered contaminated image with defects, a kernel radius of $r=20$ was used and was repeated 100 times.

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
        \label{fig:inference_DefectSimulationDust_type1}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
        \caption{FDR}
        \label{fig:inference_DefectSimulationDust_fdr}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image. a) shows the AUC when testing the image before/after contamination and after filtering. In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination. The filter used a kernel radius of 20. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The box plot summarise the 100 repeats of the experiment.}
  \label{fig:inference_DefectSimulationDust}
\end{figure}

>>>>

An experiment was conducted to investigate the specificity of the test before and after filtering. A $256\times 256$ Gaussian image with speckle defect with density $\pi_1=0.1$ and various values of $\mu_1$ were investigated. The AUC, type 1 error, type 2 error and FDR were measured when testing on an image with a defect before and after contamination and then after filtering with the contamination. A kernel radius of $r=20$ was used and was repeated 100 times by simulating another image.

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
        \label{fig:inference_DefectSimulationDust_type1}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
        \caption{FDR}
        \label{fig:inference_DefectSimulationDust_fdr}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image. In a), the upper/lower dot dashed line shows the resulting mean AUC when testing on a defected image before/after contamination respectively. In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination. The filter used a kernel radius of 20. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The box plot summarise the 100 repeats of the experiment.}
  \label{fig:inference_DefectSimulationDust}
\end{figure}
